% ============================================================
% Section: Augmenting the Moment System with Always-Treated
%          Cohorts as Bias-Corrected Controls
%
% Required packages: amsmath, amssymb
% ============================================================

\subsection{Augmenting the Moment System with Always-Treated Controls}
\label{subsec:always_treated_moments}

Let $\mathcal{G}_1$ denote the set of cohorts with at least one
pre-treatment observation in the sample (within-sample cohorts) and
$\mathcal{G}_0$ the set of cohorts treated before the sample begins
(always-treated cohorts). Partition the CATT vector as
$\beta = (\beta_1^\top, \beta_2^\top)^\top$, where $\beta_1$ collects
CATTs for $\mathcal{G}_1$ and $\beta_2$ collects CATTs for
$\mathcal{G}_0$. The baseline GMM system uses only not-yet-treated
controls and recovers $\beta_1$ via $Q_{11}\beta_1 \approx \Delta_1$,
with each row of $Q_{11}$ carrying a single $+1$ entry for the focal
CATT. Cohorts in $\mathcal{G}_0$ are excluded as focal units because
they have no within-sample pre-treatment periods.

They can, however, serve as \emph{controls} in bias-corrected
$2\times2$ DiD moments. For focal cohort $g\in\mathcal{G}_1$,
always-treated control cohort $c\in\mathcal{G}_0$, pre-period
$s < g$, and post-period $t\geq g$, the bias-corrected moment
satisfies, under parallel trends,
\begin{equation}
  \Delta_{g,c,s,t}
  = \mathrm{CATT}(g,t)
    - \bigl[\mathrm{CATT}(c,t) - \mathrm{CATT}(c,s)\bigr]
    + \varepsilon_{g,c,s,t}.
  \label{eq:biascorr_moment}
\end{equation}
Stacking these with the baseline moments yields the augmented system
\begin{equation}
  \begin{pmatrix} Q_{11} & 0 \\ Q_{21} & Q_{22} \end{pmatrix}
  \begin{pmatrix} \beta_1 \\ \beta_2 \end{pmatrix}
  \approx
  \begin{pmatrix} \Delta_1 \\ \Delta_2 \end{pmatrix},
  \label{eq:augmented_system}
\end{equation}
where $Q_{21}$ carries $+1$ entries on $\mathrm{CATT}(g,t)$ and each
row of $Q_{22}$ encodes the first difference
$-\mathrm{CATT}(c,t)+\mathrm{CATT}(c,s)$.

\paragraph{Informational content for within-sample CATTs.}
The additional moments carry genuine identifying information for
$\beta_1$ through $Q_{21}$. To see this, consider two
bias-corrected moments sharing the same control $c$ and focal cohort
$g$ but differing in the post-period:
\begin{align}
  \Delta_{g,c,s,t_1} - \Delta_{g,c,s,t_2}
  &= \bigl[\mathrm{CATT}(g,t_1) - \mathrm{CATT}(g,t_2)\bigr]
     - \bigl[\mathrm{CATT}(c,t_1) - \mathrm{CATT}(c,t_2)\bigr].
  \label{eq:diff_moments}
\end{align}
The right-hand $\beta_2$ term is a difference of always-treated
CATTs across calendar time, which is identified from
\eqref{eq:biascorr_moment} even when levels are not (see below).
Equation~\eqref{eq:diff_moments} therefore constitutes an additional
constraint on the \emph{dynamics} of $\mathrm{CATT}(g,\cdot)$ across
post-treatment horizons. These constraints are not spanned by the
$Q_{11}$ rows, which identify each CATT level independently, and
hence contribute incremental identifying variation for $\beta_1$.

\paragraph{Rank deficiency and normalization.}
Every row of $Q_{22}$ encodes a first difference of $\beta_2$, so the
vector $\mathbf{1}$ lies in its null space: adding a cohort-specific
constant $\lambda_c$ to all CATTs of cohort $c$ leaves
$Q_{22}\beta_2$ unchanged. Consequently, the augmented
system~\eqref{eq:augmented_system} identifies $\beta_2$ only up to a
per-cohort level shift. Recovering CATT levels for always-treated
cohorts requires one normalization per cohort in $\mathcal{G}_0$
--- for instance, setting $\mathrm{CATT}(c,t_0)$ to an externally
motivated value at some anchor period $t_0$, or invoking a parametric
restriction on the effect trajectory.

\paragraph{Efficiency gain for within-sample CATTs.}
Once a normalization is imposed, the augmented GMM estimator for
$\beta_1$ draws on a strictly larger set of valid moment conditions
than the baseline. By the efficiency bound for GMM
\citep{hansen1982}, adding valid moments cannot increase asymptotic
variance; the gain is nonzero whenever the residuals of the
bias-corrected moments are not perfectly collinear with the column
space of $Q_{11}$, which holds generically when always-treated
cohorts exhibit distinct outcome dynamics relative to within-sample
cohorts. In settings where the baseline moment system already
provides rich identification of $\beta_1$, the marginal efficiency
gain is likely modest; its value is greatest for early within-sample
cohorts, whose pre-treatment window is short and whose baseline
moments are therefore most sparse.

