\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{parskip}

\onehalfspacing

\title{Identification Assumptions, Error Covariance, and Inference\\
       in the Staggered Difference-in-Differences Literature:\\
       A Survey of Six Key Papers}
\author{Arora \& Bijani (2026)\\
        \small{Internal Research Note}}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

% ============================================================
\section{Introduction}
% ============================================================

Two interconnected design choices determine whether staggered
difference-in-differences estimates are valid and efficient:
the \textit{identification assumptions} that justify a causal interpretation
of the DiD estimand, and the \textit{error covariance structure} that governs
the precision and validity of inference.
This note surveys six influential papers through both lenses simultaneously.

This note surveys six influential papers in the staggered DiD literature:

\begin{enumerate}
  \item \citet{callaway2021difference} --- Difference-in-differences with multiple
        time periods.
  \item \citet{dechaisemartin2023twoway} --- Two-way fixed effects and
        difference-in-differences with heterogeneous treatment effects: a survey.
  \item \citet{gardner2024twostage} --- Two-stage differences in differences.
  \item \citet{sun2021estimating} --- Estimating dynamic treatment effects in event
        studies with heterogeneous treatment effects.
  \item \citet{wooldridge2025twoway} --- Two-way fixed effects, the two-way Mundlak
        regression, and difference-in-differences estimators.
  \item \citet{borusyak2024revisiting} --- Revisiting event-study designs: robust
        and efficient estimation.
\end{enumerate}

For each paper we address five questions:
\begin{itemize}
  \item What are the core identification assumptions (parallel trends, no
        anticipation, overlap, treatment irreversibility)?
  \item What structure is placed on the error covariance (diagonal,
        block-diagonal, fully general)?
  \item What variance estimator is recommended (cluster-robust, bootstrap,
        analytical)?
  \item Is an efficient (GLS-type) estimator proposed that exploits $\Sigma$?
  \item What caveats or special cases are highlighted (few clusters,
        cross-sectional dependence, heteroskedasticity)?
\end{itemize}

% ============================================================
\section{Paper-by-Paper Summaries}
% ============================================================

% ------------------------------------------------------------
\subsection{Callaway and Sant'Anna (2021)}
% ------------------------------------------------------------

\paragraph{Identification assumptions.}
\citet{callaway2021difference} rest identification on four conditions.
\begin{enumerate}
  \item \textbf{Conditional parallel trends.}
        For each treated cohort $g$ and post-treatment period $t \geq g$,
        the average change in untreated potential outcomes from the base
        period to $t$ is the same for cohort $g$ and the never-treated group,
        conditional on pre-treatment covariates $X$:
        \[
          \mathbb{E}[Y_t(0) - Y_{t'}(0) \mid G = g,\, X]
          \;=\;
          \mathbb{E}[Y_t(0) - Y_{t'}(0) \mid G = \infty,\, X].
        \]
        When no covariates are included this reduces to the standard
        (unconditional) parallel trends assumption.
        Conditioning on $X$ relaxes the assumption to hold only within
        covariate strata.

  \item \textbf{No anticipation.}
        Treatment does not affect potential outcomes before it is received:
        $Y_t(g) = Y_t(0)$ for all $t < g$.
        This ensures pre-treatment outcomes are valid counterfactuals.

  \item \textbf{Overlap.}
        For each cohort $g$ and covariate value $x$, the probability of
        belonging to cohort $g$ is bounded away from zero and one:
        $0 < \Pr(G = g \mid X = x) < 1$.
        This guarantees that treated and comparison units are comparable.

  \item \textbf{Staggered irreversibility (absorbing treatment).}
        Once a unit is treated it remains treated in all subsequent periods.
        Units that are never treated ($G = \infty$) serve as the clean
        comparison group.
        The paper also allows not-yet-treated units as controls, in which
        case parallel trends is required only relative to that sub-population.
\end{enumerate}
These assumptions are considerably weaker than those required for TWFE
consistency: parallel trends need hold only for each $(g, t)$ pair, not
across all cohorts simultaneously, and treatment effects may be fully
heterogeneous across cohorts, time, and covariates.

\paragraph{Error structure.}
\citet{callaway2021difference} assume that units $i = 1, \ldots, N$ are drawn
i.i.d.\ from the population.
This imposes \textit{cross-sectional independence}: the $N \times N$ block of the
covariance matrix corresponding to distinct units is zero.
Within a unit, however, the covariance matrix $\Sigma_i$ over the $T$ time periods
is left \textit{completely unrestricted}.
The aggregate covariance matrix is therefore block-diagonal with $N$ blocks of
dimension $T \times T$, where each block is an arbitrary positive semi-definite
matrix.

\paragraph{Variance estimator.}
Standard errors are derived via the \textbf{influence-function (IF) approach}.
For each ATT$(g,t)$ estimand, the authors derive an influence function
$\psi_{it}(g,t)$ at the unit level.
The asymptotic variance is then estimated by averaging the squared IFs across
units, which automatically delivers a \textbf{cluster-robust standard error}
at the unit level and is valid under the arbitrary within-unit serial
correlation permitted by the block-diagonal structure.
For simultaneous (uniform) inference across multiple $(g,t)$ cells, they
recommend the \textbf{multiplier (wild) bootstrap}, which resamples i.i.d.\
multipliers at the unit level and thereby preserves within-unit temporal
dependence.

\paragraph{GLS / efficiency.}
No efficient GLS estimator is proposed.
The doubly-robust estimator achieves the semiparametric efficiency bound for
each ATT$(g,t)$ within the class of estimators satisfying their identification
assumptions, but it does not model or exploit the within-unit covariance
$\Sigma_i$.

\paragraph{Caveats.}
When the number of treated cohorts is small, multiplier bootstrap critical values
can under-cover because bootstrap quantiles of the maximum statistic are poorly
estimated with few groups.
In such cases, the authors recommend clustering at the treatment-cohort level
(more conservative) or using randomisation inference.

% ------------------------------------------------------------
\subsection{De Chaisemartin and d'Haultfoeuille (2023)}
% ------------------------------------------------------------

\paragraph{Identification assumptions.}
As a survey, \citet{dechaisemartin2023twoway} discuss assumptions for multiple
estimators.
For their own DID$_M$ estimator, the core conditions are:
\begin{enumerate}
  \item \textbf{Parallel trends for switchers and non-switchers.}
        Units that change treatment status between two consecutive periods
        (``switchers'') share the same counterfactual trend in untreated
        potential outcomes as stable units over the same interval.
        Unlike \citet{callaway2021difference}, this is stated as a
        \textit{binary period-by-period} condition rather than over a
        multi-period baseline.

  \item \textbf{Strict exogeneity.}
        Treatment assignment is uncorrelated with the idiosyncratic error
        in each period, conditional on unit and time fixed effects.

  \item \textbf{No anticipation.}
        Current outcomes are not affected by future changes in treatment status.

  \item \textbf{No-sign-change (for aggregation).}
        When aggregating DID$_M$ across groups and periods, the authors assume
        treatment effects do not change sign across the aggregated cells
        (i.e., all effects are non-negative or all are non-positive within
        the aggregation window).
        This condition is needed to interpret the aggregated DID$_M$ as an
        ATT rather than a sign-ambiguous mixture.
\end{enumerate}
The survey also catalogues the assumptions of TWFE-based estimators and
explains why they fail under treatment effect heterogeneity: TWFE implicitly
requires that the treatment effect is constant across all cohorts and periods
when used without cohort-time interactions, which is a much stronger assumption
than any of the above.

\paragraph{Error structure.}
As a survey, \citet{dechaisemartin2023twoway} do not impose a single covariance
assumption across all reviewed estimators.
For their own DID$_M$ and related estimators, the maintained assumption is
cross-sectional independence with unrestricted within-group serial correlation
--- the same block-diagonal structure as \citet{callaway2021difference}.
The survey prominently cites \citet{bertrand2004much}, who document that
ignoring within-unit serial correlation in TWFE leads to severely
under-estimated standard errors in long panels, because the pre- and
post-treatment group means are highly correlated within units.

\paragraph{Variance estimator.}
For their DID$_M$ estimator, the authors use \textbf{influence-function-based
standard errors} clustered at the (group, period) level.
For the broader class of estimators reviewed, they recommend clustering at the
highest feasible level (typically the unit or treatment-group level) to guard
against serial correlation.

\paragraph{GLS / efficiency.}
Not addressed.
The paper's focus is identification and bias correction for heterogeneous
treatment effects rather than efficiency.

\paragraph{Caveats.}
The \textbf{few-clusters problem} receives substantial attention.
When the number of treated groups is small (fewer than roughly 20),
cluster-robust standard errors from OLS/WLS have poor finite-sample coverage.
The authors recommend the wild cluster bootstrap or randomisation inference
as alternatives.
They also note that heterogeneous treatment effects can interact with
unbalanced panel structures to amplify the bias from ignoring serial
correlation.

% ------------------------------------------------------------
\subsection{Gardner, Thakral, To and Luther (2024)}
% ------------------------------------------------------------

\paragraph{Identification assumptions.}
\citet{gardner2024twostage} rest identification on three conditions.
\begin{enumerate}
  \item \textbf{Linear factor model for untreated potential outcomes.}
        The untreated potential outcome satisfies
        $Y_{it}(0) = \alpha_i + \lambda_t + \varepsilon_{it}$,
        where $\alpha_i$ and $\lambda_t$ are unit and time fixed effects.
        This is the standard two-way fixed effects (TWFE) parallel-trends
        assumption in regression form.
        It implies that in the absence of treatment, each unit's outcome
        follows the same time trend up to a unit-specific level.

  \item \textbf{No anticipation.}
        Pre-treatment outcomes are equal to untreated potential outcomes:
        $Y_{it} = Y_{it}(0)$ for all $t$ before unit $i$ is first treated.
        This is required for the first-stage regression on untreated
        observations to consistently estimate $\alpha_i$ and $\lambda_t$.

  \item \textbf{Correct first-stage specification.}
        The unit and time fixed effects in the first stage span the full
        variation in untreated potential outcomes.
        If additional covariates or group-specific trends enter
        $Y_{it}(0)$, the first stage must include them; otherwise the
        second-stage treatment-effect estimate is biased.
\end{enumerate}
A notable feature of this paper is that, under these assumptions,
treatment effects may be \textit{fully heterogeneous} across units and time.
The two-stage design ensures that such heterogeneity does not contaminate the
first stage (which uses only untreated observations) or the second stage
(which directly estimates the treatment effect as the residual gap).

\paragraph{Error structure.}
\citet{gardner2024twostage} assume cross-sectional independence with arbitrary
within-unit serial correlation (block-diagonal $\Sigma$).
A subtle additional consideration arises from the two-stage structure: the
first-stage regression of outcomes on unit and time fixed effects uses only
the untreated observations.
The resulting residual for the second stage is therefore a function of all
untreated observations, creating a nuisance dependence across units that must
be handled carefully in the variance derivation.

\paragraph{Variance estimator.}
The estimator is cast as a \textbf{GMM estimator}, which delivers a natural
\textbf{cluster-robust sandwich variance} formula that accounts for both stages.
A key result is that the ``naive'' second-stage clustered standard error ---
obtained by simply clustering the OLS residuals from the second stage while
ignoring first-stage uncertainty --- is \textit{asymptotically valid} when the
first-stage model is correctly specified, because the first-stage estimation
error washes out in large samples.
Under misspecification or heterogeneous treatment effects, the full two-stage
sandwich correction is required.

\paragraph{GLS / efficiency.}
No efficient GLS estimator is proposed.
The authors note that efficiency improvements from modelling $\Sigma$ are
possible but leave this to future work.

\paragraph{Caveats.}
The asymptotic validity of the naive second-stage SE relies on correctly
specifying the first-stage potential outcome model.
If the first-stage fixed-effect structure is misspecified (e.g., treatment
anticipation), first-stage uncertainty becomes non-negligible even asymptotically.

% ------------------------------------------------------------
\subsection{Sun and Abraham (2021)}
% ------------------------------------------------------------

\paragraph{Identification assumptions.}
\citet{sun2021estimating} require the following conditions for their
interaction-weighted (IW) estimator to identify cohort-specific
average treatment effects on the treated (CATT).
\begin{enumerate}
  \item \textbf{Parallel trends by cohort.}
        For each treated cohort $g$ and every period $t$, the average change
        in untreated potential outcomes from the pre-treatment base period is
        the same for cohort $g$ and the never-treated (or not-yet-treated)
        units:
        \[
          \mathbb{E}[Y_{it}(0) - Y_{il}(0) \mid G_i = g]
          \;=\;
          \mathbb{E}[Y_{it}(0) - Y_{il}(0) \mid G_i = \infty],
          \quad l < g \leq t.
        \]
        This is stated cohort-by-cohort, allowing heterogeneous parallel-trends
        violations across cohorts to be separately testable.

  \item \textbf{No anticipation.}
        Treatment does not affect outcomes before it begins:
        $Y_{it}(g) = Y_{it}(0)$ for all $t < g$.
        The TWFE specification they study includes pre-treatment ``leads''
        precisely to test this condition.

  \item \textbf{Staggered irreversibility.}
        Treatment adoption is absorbing: units do not de-select from treatment.
        This, combined with parallel trends, identifies the CATT for each
        cohort $g$ at each post-treatment time $t \geq g$.

  \item \textbf{Existence of a clean comparison group.}
        A never-treated or not-yet-treated comparison group must exist and
        have positive probability mass, ensuring that the cohort-specific
        ATTs are identified from valid DiD comparisons.
\end{enumerate}
The paper's key insight is that standard TWFE with event-time dummies
\textit{fails} to recover the CATTs even when all four conditions hold,
because the OLS coefficients on the leads and lags are contaminated by
treatment effects from other cohorts.
Their IW estimator explicitly cleans these contaminations.

\paragraph{Error structure.}
\citet{sun2021estimating} adopt a standard linear panel model with no special
structure on the error covariance beyond what is needed for OLS consistency.
Cross-sectional independence is assumed; within-unit temporal dependence is
permitted but not modelled.

\paragraph{Variance estimator.}
Because their interaction-weighted (IW) estimator is a linear transformation of
OLS coefficients from a regression with cohort $\times$ time dummy interactions,
\textbf{standard cluster-robust standard errors from OLS apply directly}.
No separate asymptotic derivation is needed: the delta-method applied to the
OLS covariance matrix delivers the variance of the weighted average of
cohort-specific ATTs.
Clustering at the unit level handles within-unit serial correlation.

\paragraph{GLS / efficiency.}
Not discussed.
The paper's contribution is the identification of a clean estimand that avoids
contamination from heterogeneous effects in TWFE event studies, rather than
an improvement in efficiency or a new inference procedure.

\paragraph{Caveats.}
Because the IW estimator inherits the inference properties of TWFE OLS,
it shares TWFE's sensitivity to heteroskedasticity and serial correlation
when standard (non-cluster-robust) standard errors are used.
The paper offers no guidance on inference with few clusters.

% ------------------------------------------------------------
\subsection{Wooldridge (2025)}
% ------------------------------------------------------------

\paragraph{Identification assumptions.}
\citet{wooldridge2025twoway} embed the DiD problem in the correlated random
effects (CRE) / Mundlak framework.
The central conditions are:
\begin{enumerate}
  \item \textbf{Two-way Mundlak (TWM) projection.}
        The unit fixed effect $\alpha_i$ is modelled as a linear projection
        onto within-unit means of all time-varying regressors
        (including cohort-time treatment indicators):
        \[
          \alpha_i \;=\; \xi \;+\; \bar{X}_i'\gamma \;+\; v_i,
          \qquad \mathbb{E}[v_i \mid \bar{X}_i] = 0.
        \]
        This replaces the standard fixed-effects ``demeaning'' with an
        explicit regression, which makes the identification conditions
        transparent and allows for random-effects efficiency gains.

  \item \textbf{Strict exogeneity of treatment.}
        Conditional on $\alpha_i$, $\lambda_t$, and $X_{it}$, the treatment
        indicator is uncorrelated with the idiosyncratic error in all periods
        (past, present, and future).
        This is standard TWFE strict exogeneity.

  \item \textbf{No anticipation.}
        Cohort indicators are defined by first treatment date; future treatment
        does not affect current outcomes conditional on the unit and time effects.

  \item \textbf{Parallel trends via cohort--time interactions.}
        The extended TWFE (ETWFE) specification includes a full set of
        cohort $\times$ calendar-time interaction dummies for post-treatment
        periods.
        These interactions allow the treatment effect to be fully heterogeneous
        across cohorts and time without violating identification, provided
        parallel trends holds \textit{on average} within each cohort.

  \item \textbf{Full-rank design matrix.}
        The cohort--time interaction cells must each have positive mass so
        that the ETWFE OLS is identified.
        Thin cells (small cohort sizes) reduce precision but do not violate
        identification.
\end{enumerate}
A key contribution relative to earlier work is demonstrating that the TWFE
estimator, the Mundlak regression, and the ETWFE regression all produce
numerically identical estimates of the aggregated ATT under the same
parallel-trends assumption --- the three formulations are algebraically
equivalent, not just asymptotically so.

\paragraph{Error structure.}
\citet{wooldridge2025twoway} works within the \textit{correlated random effects}
(CRE) / two-way Mundlak (TWM) framework, which adds cohort-period means of
time-varying covariates to absorb level correlations between unit effects and
regressors.
The residual idiosyncratic error $\varepsilon_{it}$ after the Mundlak projection
is allowed to have arbitrary within-unit serial correlation.
For inference via pooled OLS, the covariance is treated as block-diagonal.
For GLS estimation, Wooldridge allows more structured within-unit covariances,
including AR(1) and equicorrelated (random-effects) structures.

\paragraph{Variance estimator.}
For pooled OLS on the extended TWFE (ETWFE) or TWM specification, the
recommendation is \textbf{cluster-robust standard errors at the unit level},
valid for large $N$ regardless of $T$ and robust to arbitrary within-unit serial
dependence.
In large-$T$ contexts where $T / N$ is non-negligible, time-series HAC
corrections may be preferred.

\paragraph{GLS / efficiency.}
This is the most substantive treatment of efficiency among the first five papers.
Wooldridge explicitly derives conditions under which \textbf{feasible GLS (FGLS)}
on the ETWFE specification is more efficient than pooled OLS.
When $\Sigma$ follows an AR(1) or equicorrelated structure and is correctly
specified, FGLS with estimated $\hat{\Sigma}$ achieves asymptotic efficiency gains.
He notes that cohort-time cell sizes are important: when cohort sizes are small,
the ATT estimator from ETWFE has high variance, and efficiency-weighted
aggregation via GLS can be substantially more precise.
Even under misspecification of $\Sigma$, FGLS is consistent; only efficiency
is lost.

\paragraph{Caveats.}
The Mundlak device controls for correlated random effects but does not
fully account for all sources of within-unit serial correlation in
$\varepsilon_{it}$.
Post-Mundlak residuals may still exhibit serial dependence, so clustering
remains necessary even after FGLS.

% ------------------------------------------------------------
\subsection{Borusyak, Jaravel and Spiess (2024)}
% ------------------------------------------------------------

\paragraph{Identification assumptions.}
\citet{borusyak2024revisiting} identify causal effects under three core
conditions.
\begin{enumerate}
  \item \textbf{Parallel trends / exogenous treatment timing.}
        Untreated potential outcomes follow a linear two-way factor structure:
        \[
          Y_{it}(0) \;=\; \alpha_i \;+\; \lambda_t \;+\; \varepsilon_{it},
        \]
        where $\alpha_i$ and $\lambda_t$ are unit and time fixed effects and
        $\varepsilon_{it}$ is mean-zero conditional on treatment history.
        This is the standard TWFE parallel-trends assumption.
        Importantly, the authors state this as an assumption on the
        \textit{potential outcome model}, not as a conditional mean
        restriction on observed data, which makes the efficiency analysis
        tractable.

  \item \textbf{No anticipation.}
        Pre-treatment observed outcomes equal untreated potential outcomes:
        $Y_{it} = Y_{it}(0)$ for all $t$ before treatment begins.
        This is required for the control-outcome model to be estimated
        consistently from pre-treatment data.

  \item \textbf{Staggered irreversibility.}
        Treatment is absorbing: once unit $i$ is treated at time $g_i$,
        it remains treated in all subsequent periods.
        Together with no anticipation, this identifies the ATT$(g, t)$
        for all post-treatment $(g, t)$ pairs.
\end{enumerate}
Beyond these three, the \textbf{efficient} (GLS) estimator requires an
additional assumption:
\begin{enumerate}
  \setcounter{enumi}{3}
  \item \textbf{Correct specification of the control outcome model.}
        The unit and time fixed effects fully capture the variation in
        $Y_{it}(0)$.
        If the true model includes additional covariates or group-specific
        trends, the imputation step will be biased unless the first stage
        is augmented accordingly.
\end{enumerate}
A distinctive feature of this paper is framing identification as a
\textit{model} for the untreated potential outcome rather than as a
selection-on-observables restriction.
This framing naturally leads to the imputation estimator: fit the model to
control observations, impute $\hat{Y}_{it}(0)$ for treated observations,
and take the average gap $Y_{it}(1) - \hat{Y}_{it}(0)$ as the ATT estimate.

\paragraph{Error structure.}
\citet{borusyak2024revisiting} provide the most explicit and general treatment of
the error covariance among all six papers.
They write the untreated potential outcome as
\[
  Y_{it}(0) = \alpha_i + \lambda_t + \varepsilon_{it},
\]
where the idiosyncratic error $\varepsilon_{it}$ is allowed to have:
\begin{itemize}
  \item \textbf{Arbitrary within-unit serial correlation}: $\mathrm{Var}(\varepsilon_i)
        = \Sigma_i$, a $T \times T$ positive definite matrix specific to unit $i$.
  \item \textbf{Heteroskedasticity across units}: $\Sigma_i$ may differ by unit.
  \item \textbf{Cross-sectional independence}: units are i.i.d.\ draws from the
        population; no spatial, network, or cross-sectional dependence is
        accommodated.
\end{itemize}

\paragraph{Variance estimator.}
Two variance estimators are derived:
\begin{enumerate}
  \item \textbf{Cluster-robust sandwich estimator.}
        Valid under cross-sectional independence with arbitrary $\Sigma_i$.
        This is their ``robust'' standard error and is analogous to
        heteroskedasticity-and-autocorrelation-consistent (HAC) variance
        estimation at the unit (cluster) level.
  \item \textbf{Efficient (GLS-based) sandwich estimator.}
        For the efficient imputation estimator, they propose estimating a common
        $\hat{\Sigma}$ from pre-treatment residuals (assuming $\Sigma_i = \Sigma$
        for all $i$), then constructing a feasible GLS sandwich variance.
        This estimator is consistent even under mild misspecification of $\Sigma$,
        because the sandwich form corrects for model error.
\end{enumerate}

\paragraph{GLS / efficiency.}
This is the paper's central methodological contribution on the inference side.
The authors prove that the \textbf{imputation-based GLS estimator achieves the
semiparametric Cram\'{e}r--Rao lower bound} for the ATT$(g,t)$ under their model.
The argument proceeds as follows:
\begin{enumerate}
  \item The untreated potential outcome model is fitted to control observations
        by GLS using the estimated $\hat{\Sigma}$.
  \item Counterfactual outcomes for treated units are imputed from this model.
  \item The treatment effect is the gap between observed and imputed outcomes,
        averaged with GLS weights.
\end{enumerate}
They show that estimators based on OLS (including
\citealt{callaway2021difference},
\citealt{sun2021estimating}, and
\citealt{gardner2024twostage})
are \textit{not} efficient because they do not exploit the within-unit
covariance structure.
The efficiency gain is substantial when within-unit serial correlation is high
or when unit-level variances are heterogeneous.

\paragraph{Caveats.}
Estimating $\Sigma$ consistently from pre-treatment residuals requires a
sufficiently long pre-treatment window ($T_{\text{pre}} \gg T_{\text{post}}$).
With short panels, the plug-in GLS estimator may be more variable than OLS
in finite samples, eroding the asymptotic efficiency gain.
The efficiency result is established under \textit{homogeneous} $\Sigma$ across
units; with heterogeneous $\Sigma_i$ the GLS estimator remains consistent but
loses the formal Cram\'{e}r--Rao guarantee.
Cross-sectional dependence (spatial, network) is not addressed.

% ============================================================
\section{Comparative Summary}
% ============================================================

\subsection{Identification Assumptions}

Table~\ref{tab:assumptions} summarises the identification conditions imposed
by each paper.
Several patterns emerge.
First, all six papers require some form of \textbf{parallel trends} for
untreated potential outcomes, but they differ in whether the condition is
stated unconditionally (Wooldridge, Borusyak et al., Gardner et al.),
conditionally on covariates (Callaway \& Sant'Anna), or period-by-period
for switchers (De Chaisemartin \& d'Haultfoeuille).
Second, \textbf{no anticipation} is universal.
Third, \textbf{absorbing treatment} (staggered irreversibility) is assumed in
all but De Chaisemartin \& d'Haultfoeuille (2023), whose DID$_M$ allows
treatment switching.
Fourth, only \citet{callaway2021difference} explicitly require an \textbf{overlap}
condition; the others implicitly assume sufficient comparison units exist but
do not formalise the overlap requirement.

\begin{table}[ht]
\centering
\caption{Identification Assumptions Across Six DiD Papers}
\label{tab:assumptions}
\renewcommand{\arraystretch}{1.4}
\begin{tabularx}{\textwidth}{@{}lXccccc@{}}
\toprule
\textbf{Paper}
  & \textbf{Parallel trends form}
  & \textbf{No antic.}
  & \textbf{Overlap}
  & \textbf{Absorbing}
  & \textbf{Het.\ TE}
  & \textbf{Strict exog.} \\
\midrule
Callaway \& Sant'Anna (2021)
  & Conditional on $X$, cohort-by-cohort
  & \checkmark & \checkmark & \checkmark & \checkmark & --- \\
De Chaisemartin \& d'Haultfoeuille (2023)
  & Period-by-period for switchers
  & \checkmark & --- & --- & \checkmark & \checkmark \\
Gardner et al.\ (2024)
  & TWFE linear factor model
  & \checkmark & --- & \checkmark & \checkmark & --- \\
Sun \& Abraham (2021)
  & Cohort-by-cohort, unconditional
  & \checkmark & \checkmark & \checkmark & \checkmark & --- \\
Wooldridge (2025)
  & Via Mundlak CRE projection
  & \checkmark & --- & \checkmark & \checkmark & \checkmark \\
Borusyak et al.\ (2024)
  & TWFE potential outcome model
  & \checkmark & --- & \checkmark & \checkmark & --- \\
\bottomrule
\multicolumn{7}{@{}l}{\footnotesize \checkmark = explicitly assumed; --- = implicit
or not formally stated.}\\
\multicolumn{7}{@{}l}{\footnotesize ``Het.\ TE'' = heterogeneous treatment effects
explicitly allowed.}\\
\end{tabularx}
\end{table}

\subsection{Error Covariance and Inference}

Table~\ref{tab:summary} consolidates the inference-related dimensions across all six papers.

\begin{table}[ht]
\centering
\caption{Error Covariance Treatment Across Six DiD Papers}
\label{tab:summary}
\renewcommand{\arraystretch}{1.4}
\begin{tabularx}{\textwidth}{@{}lXXcc@{}}
\toprule
\textbf{Paper} & \textbf{Error covariance assumed} & \textbf{SE recommendation}
  & \textbf{GLS?} & \textbf{Efficiency bound?} \\
\midrule
Callaway \& Sant'Anna (2021)
  & Block-diagonal; unrestricted within-unit $\Sigma_i$
  & Influence-function; multiplier bootstrap for joint inference
  & No & No \\
De Chaisemartin \& d'Haultfoeuille (2023)
  & Block-diagonal; unrestricted within-unit
  & IF-based; wild bootstrap for few clusters
  & No & No \\
Gardner et al.\ (2024)
  & Block-diagonal; unrestricted within-unit
  & GMM cluster-robust sandwich (two-stage corrected)
  & No & No \\
Sun \& Abraham (2021)
  & Block-diagonal; unrestricted within-unit
  & Standard OLS cluster-robust at unit level
  & No & No \\
Wooldridge (2025)
  & Block-diagonal; AR(1) or equicorrelated for FGLS
  & Cluster-robust OLS; FGLS for efficiency
  & Yes & No \\
Borusyak et al.\ (2024)
  & Block-diagonal; unrestricted $\Sigma_i$; heteroskedastic
  & Cluster-robust sandwich; GLS sandwich for efficient version
  & \textbf{Yes} & \textbf{Yes} \\
\bottomrule
\end{tabularx}
\end{table}

% ============================================================
\section{Key Takeaways}
% ============================================================

\begin{enumerate}

  \item \textbf{Universal cross-sectional independence.}
        All six papers assume that units are independent across one another.
        None addresses spatial correlation, network dependence, or other
        forms of cross-sectional dependence.
        This is an important gap: in many empirical applications (regional
        policy, financial markets, network effects) cross-unit dependence
        is plausible and could invalidate standard inference.

  \item \textbf{Universal within-unit flexibility.}
        All six papers allow arbitrary within-unit serial correlation over
        time (block-diagonal $\Sigma$ with unrestricted $T \times T$ blocks).
        Cluster-robust standard errors at the unit level are the consensus
        recommendation for handling this.

  \item \textbf{Only two papers propose GLS.}
        \citet{wooldridge2025twoway} and \citet{borusyak2024revisiting} go
        beyond cluster-robust OLS to propose efficient estimators that
        exploit the within-unit covariance structure.
        Wooldridge's approach requires a parametric model for $\Sigma$
        (AR(1) or equicorrelated); Borusyak et al.\ allow a non-parametric
        $\hat{\Sigma}$ estimated from pre-treatment residuals.

  \item \textbf{Borusyak et al.\ provide the only efficiency bound.}
        Of the six papers, only \citet{borusyak2024revisiting} formally
        derive the semiparametric Cram\'{e}r--Rao lower bound for the
        ATT$(g,t)$ and prove that their imputation GLS estimator achieves it.
        The efficiency gain over OLS-based estimators can be substantial in
        long panels with high serial correlation.

  \item \textbf{The few-clusters problem is underexplored.}
        Only \citet{dechaisemartin2023twoway} and \citet{callaway2021difference}
        discuss the case where the number of treatment clusters is small.
        The other papers implicitly assume a large number of clusters, which
        may not hold in typical DiD applications where treatment is assigned
        at the state, industry, or firm level.

  \item \textbf{Implications for the GMM framework.}
        The GMM framework in \citet{arora2026gmm} explicitly models the
        moment covariance $\Omega_\phi$ using estimated autocovariances
        $\hat{\sigma}_d$ from within-unit residuals.
        This is closest in spirit to the efficient approach of
        \citet{borusyak2024revisiting}: both exploit the panel time-series
        structure of $\Sigma$ to construct efficient weights.
        Unlike Borusyak et al., however, the GMM approach additionally
        handles ``forbidden'' comparisons and imposes the linear restrictions
        of the DiD incidence matrix $Q_H$, making it applicable in designs
        where no clean ``imputation'' control group exists.

\end{enumerate}

% ============================================================
\bibliographystyle{apalike}
\bibliography{references}
% ============================================================

% Inline bibliography for self-contained document
\begin{thebibliography}{99}

\bibitem[Arora and Bijani(2026)]{arora2026gmm}
Arora, P. and Bijani, R. (2026).
\newblock Estimating treatment effects under staggered timing using {GMM}.
\newblock Working paper.

\bibitem[Bertrand et al.(2004)]{bertrand2004much}
Bertrand, M., Duflo, E., and Mullainathan, S. (2004).
\newblock How much should we trust differences-in-differences estimates?
\newblock \textit{Quarterly Journal of Economics}, 119(1):249--275.

\bibitem[Borusyak et al.(2024)]{borusyak2024revisiting}
Borusyak, K., Jaravel, X., and Spiess, J. (2024).
\newblock Revisiting event-study designs: robust and efficient estimation.
\newblock \textit{Review of Economic Studies}, 91(6):3253--3285.

\bibitem[Callaway and Sant'Anna(2021)]{callaway2021difference}
Callaway, B. and Sant'Anna, P.~H. (2021).
\newblock Difference-in-differences with multiple time periods.
\newblock \textit{Journal of Econometrics}, 225(2):200--230.

\bibitem[De~Chaisemartin and d'Haultfoeuille(2023)]{dechaisemartin2023twoway}
De~Chaisemartin, C. and d'Haultfoeuille, X. (2023).
\newblock Two-way fixed effects and differences-in-differences with
  heterogeneous treatment effects: a survey.
\newblock \textit{The Econometrics Journal}, 26(3):C1--C30.

\bibitem[Gardner et al.(2024)]{gardner2024twostage}
Gardner, J., Thakral, N., To, L.~T., and Luther, Y. (2024).
\newblock Two-stage differences in differences.
\newblock Working paper.

\bibitem[Sun and Abraham(2021)]{sun2021estimating}
Sun, L. and Abraham, S. (2021).
\newblock Estimating dynamic treatment effects in event studies with
  heterogeneous treatment effects.
\newblock \textit{Journal of Econometrics}, 225(2):175--199.

\bibitem[Wooldridge(2025)]{wooldridge2025twoway}
Wooldridge, J.~M. (2025).
\newblock Two-way fixed effects, the two-way {Mundlak} regression, and
  difference-in-differences estimators.
\newblock \textit{Empirical Economics}, 69(5):2545--2587.

\end{thebibliography}

\end{document}
